---
title: "Homework 4"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: sandstone
---
## Problem 2

Hi, this is Yunshen Bai. In this part, we will use NYC Restaurant Inspections dataset, and use different kind of plots to show the pattern in this dataset.


```{r,message=FALSE,warning=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
data(rest_inspec)
```

First, We create a box plot to show the distribution of score in five boroughs.

```{r}
rest_inspec|>
  drop_na(score,boro)|>
  filter(boro!="Missing")|>
  mutate(boro=fct_reorder(boro,score))|>
  plot_ly(y=~score,color = ~boro,type = "box",colors = "viridis")
```
From this box plox, the score in five boroughs are almost same. Therefore, the food safety status of the five boroughs is roughly the same.

Next, we want to know what kind of restaurants reported the least and the most violations. 
```{r}
rest_inspec|>
  drop_na(score)|>
  count(cuisine_description)|>
  mutate(cuisine_description=fct_reorder(cuisine_description,n))|>
  plot_ly(x=~cuisine_description,y=~n,color = ~cuisine_description,type = "bar",colors = "viridis")
```
From above bar chart, we can know that Basque restaurants reported the least violations and Chinese restaurants reported the most violations.

Finally, we want to know the relationship between zipcode and score.
```{r,message=FALSE}
rest_inspec|>
  drop_na(score,zipcode)|>
  group_by(zipcode)|>
  summarise(score=mean(score))|>
  plot_ly(x=~zipcode,y=~score,color =~score,alpha = 0.5)
```



